Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654

### 2016-06-28 WRITEUP/ms.tex
done with analysis section

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disk peaks \citep{Courteau97b}.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (\citetalias{Claeskens06a}; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
\citepalias{Brewer08a} and $H$-band \citepalias{Claeskens06a}, respectively.
The CO gas is thus of similar spatial
extent as $H$ and $I$-bands.

@@

The dust temperature from both models is similar to that of
ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K;
\citealt[hereafter C13]{Combes13a}).
We note the \fir luminosity is comparable in both models, which is
not surprising given the lack of constraints in the MIR.
For the subsequent analysis, we adopt the physical quantities
from the first model (\ie with constraints at 24\,\micron).
The choice of SED model does not affect
the derived star formation rate (SFR) given the similar \fir luminosity.
Yet, the dust mass is higher in the former but consistent within the
uncertainties.
We correct for lensing using the median magnification
factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a
 \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun
 and
 a total IR luminosity of $\sim$1.5\E{12}\,\Lsun,  implying RXJ1131 is a ULIRG.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR$_{\rm FIR}$ of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.
\defcitealias{Combes13a}{C13}
\begin{figure}[!htbp]
\centering
\includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
% WISE flux is slightly higher than the IRAC point, probably due to a smaller
% aperture used in IRAC extraction (both from archive).
% It is also not straight-forward to fit an SED model covering a wider wavelengths because of
% differential lensing.
\caption{SEDs of RXJ1131 and its lensing galaxy. The photometry is listed in \Tab{photometry}.
Best-fit SED models of the thermal dust emission towards RXJ1131
with(out) MIR constraint at 24\,$\micron$ are plotted as dashed (solid) lines.
\label{fig:SED}}
\end{figure}

@@

\subsubsection{Linewidth and Sizes} \label{sec:sizes}
A linewidth of $\Delta v_{\rm FWHM}$$\sim$600\pmm160\,\kms found from
fitting a single Gaussian
is considerably larger that those in the \citepalias{Combes13a} sample
(370\,\kms) as well as local ULIRGs
\citep[300\pmm85\,\kms, with the largest being 480\,\kms;][hereafter S97]{Solomon97a}.
%ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ≥ 1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
Yet, given the dynamic nature of these galaxies,
a CO linewidth of $\sim$600 may not be surprising.
Indeed, a linewidth of $\Delta v$ = 750\,\kms has been observed
in a local LIRG (Arp 118) \citep{SV05a}.
Such FWHM is also commonly observed in high-z starburst galaxies
\citep[780\pmm320\,\kms; \eg][]{Greve05a}.
\defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}

The CO gas in RXJ1131 is $\sim$6\pmm3\,kpc in radius (in the source plane),
which is more
extended than the sample of disk-like U/LIRGs studied by
\citet[hereafter U14]{Ueda14a}, who find an average radius of 3.5\pmm2.3\,kpc but with a range of 1.1\,$-$\,9.3\,kpc.
Such a range is consistent with the results reported by \citet{Gao99a}, where
they also find CO disks extending out to $R\sim$10\,kpc.
In contrast to the results
reported in the classical study by
\citet[hereafter DS98]{Downes98a}, who find molecular gas sizes of $R<$1\,kpc in their sample of local ULIRGs
(see also \citealt{Bryant99a} and \citealt{Iono09a}), it appears that the molecular gas in ULIRGs
can be distributed over large regions comparable to
those reported in high-z ($z$$>$\,1) galaxies \citep[$R\sim$7\,kpc;
\citetalias{Greve05a};][]{Daddi10a, Riechers11a, Ivison11a}.
While we cannot draw conclusions any evolution in the
molecular gas size
as we are only studying one
ULIRG at intermediate redshift, it appears that local ULIRGs are composed of
mergers at various stages of merging, and are therefore not
necessarily more compact than
high-z SMGs \citep[cf. \eg][]{Iono09a}.
\defcitealias{Ueda14a}{U14}
\defcitealias{Downes98a}{DS98}
\defcitealias{Ivison11a}{I11}
\defcitealias{Riechers11a}{R11}

@@

\subsubsection{Gas Mass and Gas Ratios}
% Solomon97 (ULIRGs z < 0.3): 0.4-1.5 e10 Msun
% SV05: Solomon+97: average Mgas ~7e9 Msun
% SV05: high-z: (2.5-10)e10 Msun
A total molecular gas mass of
$M_{\rm gas}^{\rm total}$ = $($1.57\pmm0.38$)$\E{10}\,\Msun is
residing within the merger system (see \Sec{caveat}).
This is comparable to those found in the
\citetalias{Combes13a} sample %(1.5\E{10}\Msun)
as well as local U/LIRGs
\citep[][\citetalias{Solomon97a}]{Sanders96a} but higher than
in local LIRGs \citepalias{Ueda14a}, as expected.
Our finding is thus consistent with previous results, where
high-z galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
and is
distributed over larger spatial extents
\citep[\eg][\citetalias{Riechers11a,Ivison11a}]{SV05a}.
% gas-to-dyn ratio
% DS98: f ~ 0.16 (but w/in disc or ring of R ~ 0.5 kpc)
% Bothwell+13: f ~ 0.3? (but over larger R)
% --> ULIRGs gas fraction is even lower if average over same scale as SMGs
% Daddi10a; Tacconi10a: f_gas ? 40% in z ? 1 discs, significantly higher than local discs (but alphaCO not same as ULIRGs)
Using the dynamical mass and the total
gas mass ($M_{\rm gas}^{\rm total}$), we find a gas mass
fraction of $f_{\rm gas-dyn}$ = 0.19\pmm0.37, which is
consistent with the results reported by \citetalias{Combes13a}:
a gas fraction of 15\% in ULIRGs at 0.2\,$<$\,$z$\,$<$\,0.4 and 24\%
in those at 0.6\,$<$\,$z$\,$<$\,1.0, and those from resolved measurements of local ULIRGs \citepalias{Downes98a}.
% This implies that the gas fraction in ULIRGs at $z$$<$\,1 is
% similar to high-z starburst galaxies, but
% lower if we average over the same spatial scales (as SMGs, which
% are more extended; \citet{Bothwell13a}).
This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
similar to those in high-$z$ starburst galaxies
\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}
as well as high-$z$ ``normal'' star-forming disc galaxies
\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a}.
\defcitealias{Daddi10a}{D10}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass,
% of $M_{\rm dust}$ = 4.0\petm{0.9}{3.3}\E{8}$(\mu_{\rm L}/5.5)\pmOne$\,\Msun,
we find a gas-to-dust ratio of
40\pmm34, which is significantly lower than the average
in the \citetalias{Combes13a} sample of $f_{\rm gas-dust}$\,=\,206, but
consistent within the scatter and also with the
sample of local ULIRGs studied by \citet[][]{Wilson08a},
with a ratio of $($50$-$70$)$.
% If we assume that most ULIRGs at the same epoch should have similar dust and
% gas content owing to their empirical scaling relations
% with the parameters in the fundamental metallicity relation \citep{Mannucci10a}
% and their respective evolutions as well as the
% well-established \LFIR--\Lp correlation \citep[\eg][]{Young91a, Sanders91a},
% the low gas-to-dust ratio of RXJ1131 compared to the
% \citetalias{Combes13a} sample may be explained
% in part due to differential lensing between the gas and the dust, leading to
% an overestimation of the dust mass via our adoption of the CO magnification
% factor, but this is
% unlikely [the dominant reason/enough to account] for the factor of $\sim$5
% discrepancy. It is thus necessary to invoke other possible explanations.
We note that the gas-to-dust ratio is only good within
within a factor of 2$-$3 as
differential lensing may exist between the gas and the dust, leading to
an under- or overestimation of the dust mass via our adoption of the CO magnification factor.

% We also note that the gas-to-dust ratio of ULIRGs
% varies widely in the literature, ranging from 50 to $>$200.
% Such a variation can arise depending on a few factors, such as the resolution

% Alternately, this may indicate a different \alphaco conversion factor.

% The primary source of uncertainty in the gas mass is
% undeniably the conversion factor, which if all galaxy samples we
% are comparing against use the same conversion factor but that our dust-to-gas
% ratio is different (due to the Mdust), which implies different physical
% conditions.
% It thus appears that RXJ1131 is more dusty than ULIRGs at the same epoch, which may indicate different
% ISM conditions/ISM properties and potentially a different alphaCO.
% Then it might be reasonable that the alphaco = 0.8 is inappropriate in this case. A higher alpha CO (upper limit using disc value) lead to a gas mass that is $\sim$5 factors higher.
% Which seems likely to account for the discrepancy because Galactic conversion factor \citep{Papadopoulos12a} might indeed be the true conversion factor in RXJ1131.

% The secondary effect/uncertainty is the excitation condition, which we have conservatively assumed to be thermalized.
% Should a subthermal condition, we would obtain an even
% higher gas mass) and that ULIRGs have thermalized excitation up to $J$ = 3 or
% 4, so the assumption on the brightness temperature ratio should not be the
% main contribution to the discrepancy in GDR. Also how dust mass
% is highly dependent on the method (model and how the data are obtained, e.g.
% resolution) used to obtain the dust mass (e.g. Seaquist+04, finding a GDR
% affecting by a factor of $\sim$5 in the inner few kpc in some cases for
% U/LIRGs but global GDR unaffected: ). For now, assume that the dust mass
% obtained from the literature is the best (most appropriate, close to physical)
% way to obtain dust mass with the given data for their sample. Then we discuss
% the implications/reasoning/causes for a low SFE in RXJ1131.

\subsubsection{SFE and Depletion Timescales}
% CO-IR luminosity correlation

In principle, the gas consumption timescale or the star formation efficiency (SFE) furnishes information on the AGN and star-formation
triggering mechanisms.
Physically, the SFE depends on the SMBH gas
consumption time scales and on the energy injected
to the ISM by AGN feedback. High SFE may thus be indication
of a small gas reservoir that was reduced by BH accretion and outflows.
In practice, the SFE is the ratio between the \fir luminosity and CO luminosity as an indicator of the SFR per solar mass of molecular gas.

Using the far-IR luminosity definition used by
C13 (40\,$-$\,500\,$\micron$),
we find a SFE $($=\LFIR/$M_{\rm gas})$ of 58\pmm10\,\Lsun$/$\Msun,
or equivalently a depletion
timescale of $\tau$\,=\,102\pmm25\,Myr.
% Gas depletion time assuming the SF is the only way to consume the gas reservoir, and that SF continues at the current rate. Since it is likely that
% SFR will vary in such a merger situation and that the AGN will consume some of the gas, hence the gas depletion timescale should only be considered as an upper limit.
% Such an SFE is lower than other U/LIRGs (SFE: 180 +/- 160 Lsun/M \citep{Solomon97a, Combes11a}.
% The depletion timescales in the C13 sample
% of 39 galaxies between 0.2$<$$z$1.0 are $<$ 100 Myr.
% C13: SFE = 100 Lsun/Msun

% --------------------------
% SFE:
% in terms of LFIR/Mgas:
% Greve+05: 450 +/- 170 Lsun/Msun for SMG
% Solomon97a: 180 +/- 160 Lsun/Msun

@@

% SV05: local (z<0.1 spirals) of SFE < 100

@@

% Depletion time:
% Greve+05: ~40 Myr

% At high redshifts,
% SMGs the irregular, turbulent star-bursting galaxies (SFR $\sim$1\E{2}-1\E{3}\,\Msun yr\pmOne) and BzKs are the ``normal" star-forming disk galaxies (at z$\sim$1.6) with relatively lower SFE, SFR ($\sim$BLAH) and
% longer depletion time (BLAH Myr) (CW13, \citealt{Daddi10a}), but surface
% densities, SFRs, velocity dispersion very similar to local mergers (Daddi10a, Krumholz\&Dekel10, Genzel+11).
% SFE is highly dependent on the alphaCO if using ratio between the \LIR and gas mass instead of using the ratio between (far-)IR luminosity and CO luminosity.
% And the use of which alphaCO is also not well justified, especially at high-z (\ie high uncertainties on the alphaco value).

% % galactic value: 4.6
% In fact
% e.g. Daddi10a argue for an \alphaco conversion factor of 3.6\pmm0.8 for normal SF disk (BzK galaxies) at z$\sim$1.5 using kinematic analysis/dynamical model (based on the dynamical mass). Whereas \citet{Tacconi08a, Carilli10a} place an upper limit of $\sim$0.8 on high-z SMGs, leading the emergence of two star formation modes.
% Carilli+10: based on dynamical constraints

% if RXJ is intriscally low SFE:
% In terms of more recent simulations, it may be what Hopkins09a suggests that the disc can survive merge by lowering SFE in low-mass systems, allowing them to retain large gas fraction and distributing the gas to larger radii.
% Thus in Hopkins09a: 1:1 gas-riich mergers can yeild disc-dominated remantns, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.

% This unexpectedly low SFE in RXJ1131...
% % that it is indeed converting gas into stars at a lower rate.
% but as mentioned above, the possible scenario that an \alphaco of 0.8 UNIT is inappropriate here.

% \subsubsection{Conversion Factor $\alpha_{\rm CO}$}

% From the gas-to-dust ratio and SFE, it is evident that a different \alphaco conversion factor may be more appropriate for RXJ1131.

% The physical motivation/basis for deriving the gas mass from CO luminosity is
% assuming virialized (self-gravitating), non-overlapping gas cloud.
% Then \alphaco scales as $n^{1/2}/T_b$, where $n$ is the average H$_2$ number density
% in the clouds and $T_b$ is the intrinsic brightness temperature of the CO line.

% Downes,Solomon \& Radford 93, Solomon97: CO emitting gas in the centers of ULIRGs is unlikely to be virialized, but instead bound by the potential of the galaxy or from molecular gas in pressure rather than gravitational equilibrium.

% DS98: showed that alphaco is a factor of $\sim$6 smaller for local ULIRGs than for local spirals.
% Also see Scoville+97

% % also a function of metallicity (Leroy11 apj 737, 12), excitation, pressure.
% %\alphaco lower for objects with extended surface gas densities (Downes Solomon98), where gas temperature and velocity dispersion are higher.
% %While the conversion factor $(\alphaco)$ is commonly adopted as 0.8  (K \kms pc$^2$)\pmOne
% %for ULIRGs, its numerical value depends on the ISM environment (Narayanan11a).
% %For instance, it could be
% %different in a dynamically turbulent galaxy, where the gas is warmer, more excited, and denser.
% % Instead of obtaining a crude estimate
% %using the dust mass and CO luminosity, assuming a
% %gas-to-dust ratio. {\textbf but this gal. have very different GDR than others, can I even assume that? or is it
% %because of the alphaCO that is leading to the different in GDR, but others also uses the same alphaCO.
% %Also probably shouldn't do this given how poorly-constrained the Mdust is..}
% %Here we assume a gas-to-dust ratio of 72 (Sandstrom+13), based on a sample of local star-forming
% %galaxies of solar metallicities.
% %We find $\alpha_{\rm CO}$ = BLAH\pmm$(f_{\rm gas-dust}/72)$ (K \kms pc$^2$)\pmOne, where the uncertainty does not include systematic uncertainties
% %in the dust absorption coefficient $(\kappa)$ and the gas-to-dust ratio.
% % We discuss a potential different \alphaco that is more appropriate
% % for RXJ1131.

>>>>

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disk peaks \citep{Courteau97b}.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (\citetalias{Claeskens06a}; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
\citepalias{Brewer08a} and $H$-band \citepalias{Claeskens06a}, respectively.
The CO gas is thus of similar spatial
extents as in $H$ and $I$-bands.

@@

The dust temperature from both models is similar to that of
ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K;
\citealt[hereafter C13]{Combes13a}).
We note the \fir luminosity is comparable in both models, which is
not surprising given the lack of constraints in the MIR.
For the subsequent analysis, we adopt the physical quantities
from the first model (\ie with constraints at 24\,\micron).
The choice of SED model does not affect
the derived star formation rate (SFR) given the similar \fir luminosity.
Yet, the dust mass is higher in the former but consistent within the
uncertainties.
We correct for lensing using the median magnification
factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a
 \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun
 and
 a total IR luminosity of $\sim$1.5\E{12}\,\Lsun,  implying RXJ1131 is a ULIRG.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR$_{\rm FIR}$ of 120\pmm63\,\sfrU using the
standard conversion \citep{Kennicutt98a}.
\defcitealias{Combes13a}{C13}
\begin{figure}[!htbp]
\centering
\includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
% WISE flux is slightly higher than the IRAC point, probably due to a smaller
% aperture used in IRAC extraction (both from archive).
% It is also not straight-forward to fit an SED model covering a wider wavelengths because of
% differential lensing.
\caption{SEDs of RXJ1131 and its lensing galaxy. The photometry is listed in \Tab{photometry}.
Best-fit SED models of the thermal dust emission towards RXJ1131
with(out) MIR constraint at 24\,$\micron$ are plotted as dashed (solid) lines.
\label{fig:SED}}
\end{figure}

@@

\subsubsection{Linewidth and Sizes} \label{sec:sizes}
A linewidth of $\Delta v_{\rm FWHM}$$\sim$600\pmm160\,\kms found from
fitting a single Gaussian
is considerably larger that those in the \citepalias{Combes13a} sample
(370\,\kms) as well as local ULIRGs
\citep[300\pmm85\,\kms, with the largest being 480\,\kms;][hereafter S97]{Solomon97a}.
%ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ≥ 1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
Yet, given the dynamic nature of these galaxies,
a CO linewidth of $\sim$600 may not be surprising.
Indeed, a linewidth of $\Delta v$ = 750\,\kms has been observed
in a local LIRG (Arp 118) \citep{SV05a}.
Such FWHM is also commonly observed in high-$z$ starburst galaxies
\citep[780\pmm320\,\kms; \eg][]{Greve05a}.
\defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}\defcitealias{SV05a}{SV05}

The CO gas in RXJ1131 is $\sim$6\pmm3\,kpc in radius (in the source plane),
which is more
extended than the sample of disk-like U/LIRGs studied by
\citet[hereafter U14]{Ueda14a}, who find an average radius of 3.5\pmm2.3\,kpc but with a range of 1.1\,$-$\,9.3\,kpc.
Such a range is consistent with the results reported by \citet{Gao99a}, where
they also find CO disks extending out to $R\sim$10\,kpc.
In contrast to the results
reported in the classical study by
\citet[hereafter DS98]{Downes98a}, who find molecular gas sizes of $R<$1\,kpc in their sample of local ULIRGs
(see also \citealt{Bryant99a} and \citealt{Iono09a}), it appears that the molecular gas in ULIRGs
can be distributed over large regions comparable to
those reported in high-$z$ ($z$$>$\,1) galaxies \citep[$R\sim$7\,kpc;
\citetalias{Greve05a};][]{Daddi10a, Riechers11a, Ivison11a}.
While we cannot draw any conclusions on the evolution of 
molecular gas size
as we are only studying one
ULIRG at intermediate redshift, it appears that local ULIRGs are composed of
mergers at various stages of merging, and are therefore not
necessarily more compact than
high-$z$ SMGs \citep[cf. \eg][]{Iono09a}.
\defcitealias{Ueda14a}{U14}
\defcitealias{Downes98a}{DS98}
\defcitealias{Ivison11a}{I11}
\defcitealias{Riechers11a}{R11}

@@

\subsubsection{Gas Mass and Gas Ratios}
% Solomon97 (ULIRGs z < 0.3): 0.4-1.5 e10 Msun
% SV05: Solomon+97: average Mgas ~7e9 Msun
% SV05: high-z: (2.5-10)e10 Msun
A total molecular gas mass of
$M_{\rm gas}^{\rm total}$ = $($1.57\pmm0.38$)$\E{10}\,\Msun is
residing within the merger system (see \Sec{caveat}).
This is comparable to those found in the
\citetalias{Combes13a} sample %(1.5\E{10}\Msun)
as well as local U/LIRGs
\citep[][\citetalias{Solomon97a}]{Sanders96a} but higher than
in local LIRGs \citepalias{Ueda14a}, as expected.
Our finding is thus consistent with previous results, where
high-$z$ galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
and is
distributed over larger spatial extents
\citepalias[\eg][]{SV05a,Riechers11a,Ivison11a}.
% gas-to-dyn ratio
% DS98: f ~ 0.16 (but w/in disc or ring of R ~ 0.5 kpc)
% Bothwell+13: f ~ 0.3? (but over larger R)
% --> ULIRGs gas fraction is even lower if average over same scale as SMGs
% Daddi10a; Tacconi10a: f_gas ? 40% in z ? 1 discs, significantly higher than local discs (but alphaCO not same as ULIRGs)
Using the dynamical mass and the total
gas mass ($M_{\rm gas}^{\rm total}$), we find a gas mass
fraction of $f_{\rm gas-dyn}$ = 0.19\pmm0.37, which is
consistent with the results reported by \citetalias{Combes13a}:
a gas fraction of 15\% in ULIRGs at 0.2\,$<$\,$z$\,$<$\,0.4 and 24\%
in those at 0.6\,$<$\,$z$\,$<$\,1.0, and those from resolved measurements of local ULIRGs \citepalias{Downes98a}.
% This implies that the gas fraction in ULIRGs at $z$$<$\,1 is
% similar to high-z starburst galaxies, but
% lower if we average over the same spatial scales (as SMGs, which
% are more extended; \citet{Bothwell13a}).
This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
similar to those in high-$z$ ``normal'' star-forming disc galaxies
\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a} as well as
high-$z$ starburst galaxies
\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}.
\defcitealias{Daddi10a}{D10}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass,
% of $M_{\rm dust}$ = 4.0\petm{0.9}{3.3}\E{8}$(\mu_{\rm L}/5.5)\pmOne$\,\Msun,
we find a gas-to-dust ratio of
40\pmm34, which is significantly lower than the statistical average
of $f_{\rm gas-dust}$\,=\,206
in the \citetalias{Combes13a} sample but
consistent with their range of values and the
\citet[][]{Wilson08a}
sample of local ULIRGs. %$($50$-$70$)$.
% If we assume that most ULIRGs at the same epoch should have similar dust and
% gas content owing to their empirical scaling relations
% with the parameters in the fundamental metallicity relation \citep{Mannucci10a}
% and their respective evolutions as well as the
% well-established \LFIR--\Lp correlation \citep[\eg][]{Young91a, Sanders91a},
% the low gas-to-dust ratio of RXJ1131 compared to the
% \citetalias{Combes13a} sample may be explained
% in part due to differential lensing between the gas and the dust, leading to
% an overestimation of the dust mass via our adoption of the CO magnification
% factor, but this is
% unlikely [the dominant reason/enough to account] for the factor of $\sim$5
% discrepancy. It is thus necessary to invoke other possible explanations.
We note that the gas-to-dust ratio maybe biased low as
the optically thick gas is likely to be more extended than the dust, leading to
an overall lower magnification factor than the dust emission,
and thus an overestimate of the
dust mass via our adoption of the CO magnification factor.

% A direct comparison to the literature is not straightforward as the dust mass estimate
% is highly dependent on the method, \eg the model assumed, the wavelength and resolution at which the data 
% were observed. Seaquist+04 find that a GDR can be 
% affected by a factor of $\sim$5 in the inner few kpc in some cases for
% U/LIRGs but global GDR may be unaffected. If we assume that the dust mass
% obtained from the literature is obtained through the most appropriate
% way with the given data for their sample, then the main uncertainty related to the dust mass is the mass
% opacity coefficient. While the main systematic uncertainties associated with the gas mass
% are the \alphaco conversion factor and the brightness temperature ratio $R_{\rm 21}$.

There are a number of systematic uncertainties associated with this quantity, \eg
the mass opacity coefficient $\kappa$,
the \alphaco conversion factor, and the brightness temperature ratio $R_{\rm 21}$.
The fact that RXJ1131 has a lower dust-to-gas ratio 
and appears to be more dusty than most ULIRGs at the same epoch
may imply different physical
environment compared to others. If we instead use the ``Galactic" \alphaco value, 
the gas mass (and thus gas-to-dust ratio) would be $\sim$6 times higher.
On the other hand, we would also obtain a higher gas mass if 
we assume subthermal excitation between \bco and \aco line emission.
However, we expect this to be a minor effect as ULIRGs are observed to be
thermalized up to $J$ = 3 or 4.

\subsubsection{SFE and Depletion Timescales}
% CO-IR luminosity correlation
% SFE:
% in terms of LFIR/Mgas:
% Greve+05: 450 +/- 170 Lsun/Msun for SMG
% Solomon97a: 180 +/- 160 Lsun/Msun
% SV05: local (z<0.1 spirals) of SFE < 100

@@

@@

To first order, the star formation efficiency
$($SFE = \LFIR$/$$M_{\rm gas})$
indicates the \SF rate per
unit solar mass of molecular gas available in a galaxy.
Using a wavelength range of 40\,$-$\,500\,$\micron$ defined
in \citetalias{Combes13a} as the far-IR luminosity,
we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$,
which is on the low end among other U/LIRGs
% \citep[$\sim$180\pmm160 \Lsun $M_{\odot}^{-1}$;][]{Solomon97a, Combes11a}
\citep{Solomon97a, Combes11a}
but 
similar to those of
low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a}.
In constrast, a star formation efficiency of $>$100 \Lsun $M_{\odot}^{-1}$
has been reported in ULIRGs and SMGs at 0.6\,$<$\,$z$\,$<$\,3
\citep[][\citetalias{Riechers11a,Combes13a}]{Tacconi08a}.
\defcitealias{Tacconi08a}{T08}
% Depletion time:
% Greve+05: ~40 Myr
Assuming the \SF continues at the current rate without gas replenishment and is the only
way to consume the gas reservoir, this corresponds to a depletion
time of $\tau$\,=\,102\pmm25\,Myr.
Since the \SF rate is expected to vary in an interacting system and that AGN accretion
also consumes some fraction of the gas, the depletion
timescale should only be considered as an upper limit.

The SFE (using the above definition) is highly dependent on the gas mass.
Yet, the use of an ``ULIRG" \alphaco value is not well justified and 
should only be considered as a lower limit \citepalias[see][]{Solomon97a}.
It may be more appropriate to use an \alphaco closer to the ``Galactic" value in 
some ULIRGs \citep[\eg][]{Papadopoulos12a}. 
From numerical models, it is found that mergers on average have lower \alphaco values than
disk galaxies \citep{Narayanan12a}.
But since the gas temperatures and velocity dispersions in minor mergers do not deviate from 
galactic GMCs as much as in major mergers, the \alphaco may not be as extreme as 0.8\,\alphaU.
% thus the rise in CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
Hence,
we can derive an upper limit on the gas mass for RXJ1131 using the standard conversion factor.
If we have instead applied the Galactic value of 4.6\,\alphaU, 
the gas mass (and thus the SFE) would be higher by a factor of $\sim$6. 
In contrast to results in the classical study of nearby ULIRGs by \citetalias{Downes98a}, who find that
the gas mass exceeds the dynamical mass using 
the Galactic conversion factor 
(and thus inappropriate for their sample), the gas mass derived for
RXJ1131 using the Galactic value is consistent with its dynamical mass.
%Obviously, this will lead to a longer depletion time.

Alternatively, the relatively low SFE maybe intrinsic to RXJ1131.
In that case,  RXJ1131 may evolve into a disc galaxy with a small bulge component
in the context of theoretical simulations by \citet{Hopkins09a}, who suggest 
that the disc component in a progenitor galaxy can survive post-merging
by lowering the \SF efficiency, enabling a higher gas fraction to be retained and 
distributed over a larger extent.
% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.

%While the \alphaco conversion factor is commonly assumed to be 0.8\,\alphaU for
%for ULIRGs/starbursts, its numerical value depends on the ISM environment
% \citep[\eg][]{Narayanan11a}.
% For instance, it could be different in a 
% dynamically turbulent galaxy, where the gas is warmer, more excited, 
% and denser, than in a quiescent galaxy.
% In addition, the physical basis for deriving the gas mass from the CO luminosity is
% by assuming the ISM only consists of virialized, non-overlapping gas clouds, 
% which is often not true in ULIRGs \citep[][\citetalias{Solomon97, Downes98a}]{Downes93a}.
% % the CO emitting gas in the centers of ULIRGs is unlikely to be virialized, but instead bound by the potential of the galaxy or from molecular gas in pressure equilibrium rather than gravitational equilibrium.

% % DS98: lower alphaCO for objects with extended surface gas densities, where gas temperature and velocity dispersion are higher; Mgas derived from radiative transfer model instead of using standard conversion factor, which yields the \alphaco = 0.8 UNIT for local ULIRGs. 
% % Also see Scoville+97

 %As discussed in Solomon \& Vanden
 %Bout (2005), low-$z$ studies of ULIRGs have led to the
 %suggestion that the conversion factor could be several times
 %smaller (Downes et al. 1993; Bryant \& Scoville 1999, DS98). This can
 %arise in ULIRGs if the gas is concentrated in the nuclear
 %regions (as a result of dissipative galaxy merging) and the
 %molecular emission linewidths can be broadened by the galactic
 %dynamics associated with the stellar mass, not just the self-gravitating
 %gas mass as in individual GMCs in which the
 %standard conversion factor was derived. In addition, the mean
 %gas temperature and density may be different in the ULIRG
 %nuclei as a result of the intense star formation activity and since AlphaCO
 %should vary as density and temperature e.g. (Dickman et al. 1986).
 % Also should be a continuous distribution instead of a bimodal value (Narayanan+12).
 % Yet, from numerical models, it is found that mergers have lower alphaCO than
 % disk galaxies, thus we can derive an upper limit on the gas mass in the RXJ1131 merger system using a disk alphaCO factor.
% In a minor merger, the rise in gas temperatures and velocity dispersions are not as extreme as in major mergers. Hence, the rise in velocity-integrated CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
